AtmoSwing (v1.4): Analogue Technique Model for Statistical weather forecastING

### 2016-05-26 AtmoSwing - Geoscientific Model Development/template.tex
Renaming figures to insert the new ones.

\citet{Horton2012} identified that the analogy on the atmospheric circulation may not be comprehensive, and that a significant gain was obtained by considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 (Table \ref{table:R6}). The number of analogues ($N_{1}$) was not provided globally, as it was calibrated for every subregion. An equivalent structure was also optimized by means of generic algorithms (PC-4Zgo), which is the topic of another paper \citep{Horton2016b}.

@@

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig02.pdf}
	\caption{The AtmoSwing logo and its 3 modules: the Forecaster, the Viewer and the Optimizer.}
	\label{figure:logo}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig03.pdf}
	\caption{Simplified organizational chart of the AM implementation in AtmoSwing.}
	\label{figure:flowchart_modules_atmoswing}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig04.png}
	\caption{Graphical user interface of the Forecaster module. A list of different parameterizations is being processed.}
	\label{figure:atmoswing-forecaster-gui}
\end{figure}

\begin{figure*}[t]
	\includegraphics[width=18cm]{figures/fig05.png}
	\caption{Graphical user interface of the Viewer module (Elevation data from The Shuttle Radar Topography Mission (SRTM), and hydrological network from SwissTopo).}
	\label{figure:atmoswing-viewer-gui}
\end{figure*}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig06.png}
	\caption{Visualization of multiple lead times on the map (Elevation data from the SRTM, and hydrological network from SwissTopo).}
	\label{figure:atmoswing-viewer-snail}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig07.png}
	\caption{Visualization of the forecasted time series.}
	\label{figure:atmoswing-viewer-timeseries}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig08.png}
	\caption{Visualization of the forecasted precipitation distribution for a given lead time.}
	\label{figure:atmoswing-viewer-distribution}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig09.png}
	\caption{Example of a Monte\textendash Carlo analysis on the PC-2Z (Table \ref{table:R1}) AM. Results are illustrated for the 4 parameters defining the spatial window on Z500, along with the results of the sequential calibration (red cross).}
	\label{figure:monte_carlo_r1}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig10.png}
	\caption{Example of a Monte\textendash Carlo analysis on the PC-2Z-2MI (Table \ref{table:R2}) AM. Results are illustrated for the number of analogues on the first and second level of analogy, along with the results of the sequential calibration (red cross).}
	\label{figure:monte_carlo_r2}
\end{figure}

>>>>

\citet{Horton2012} identified that the analogy on the atmospheric circulation may not be comprehensive in an alpine environment, and that a significant gain was obtained by considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 (Table \ref{table:R6}). The number of analogues ($N_{1}$) was not provided globally, as it was calibrated for every subregion. An equivalent structure was also optimized by means of generic algorithms (PC-4Zgo), which is the topic of another paper \citep{Horton2016b}.

@@

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig02.pdf}
	\caption{Performance scores, for the Swiss Alps, for different AM variants on a single level of analogy \citep{Horton2012a}.}
	\label{figure:scores_1}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig03.pdf}
	\caption{Performance scores, for the Swiss Alps, for different AM variants on multiple levels of analogy \citep{Horton2012a}.}
	\label{figure:scores_2}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig04.pdf}
	\caption{The AtmoSwing logo and its 3 modules: the Forecaster, the Viewer and the Optimizer.}
	\label{figure:logo}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig05.pdf}
	\caption{Simplified organizational chart of the AM implementation in AtmoSwing.}
	\label{figure:flowchart_modules_atmoswing}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig06.png}
	\caption{Graphical user interface of the Forecaster module. A list of different parameterizations is being processed.}
	\label{figure:atmoswing-forecaster-gui}
\end{figure}

\begin{figure*}[t]
	\includegraphics[width=18cm]{figures/fig07.png}
	\caption{Graphical user interface of the Viewer module (Elevation data from The Shuttle Radar Topography Mission (SRTM), and hydrological network from SwissTopo).}
	\label{figure:atmoswing-viewer-gui}
\end{figure*}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig08.png}
	\caption{Visualization of multiple lead times on the map (Elevation data from the SRTM, and hydrological network from SwissTopo).}
	\label{figure:atmoswing-viewer-snail}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig09.png}
	\caption{Visualization of the forecasted time series.}
	\label{figure:atmoswing-viewer-timeseries}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig10.png}
	\caption{Visualization of the forecasted precipitation distribution for a given lead time.}
	\label{figure:atmoswing-viewer-distribution}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig11.png}
	\caption{Example of a Monte\textendash Carlo analysis on the PC-2Z (Table \ref{table:R1}) AM. Results are illustrated for the 4 parameters defining the spatial window on Z500, along with the results of the sequential calibration (red cross).}
	\label{figure:monte_carlo_r1}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.3cm]{figures/fig12.png}
	\caption{Example of a Monte\textendash Carlo analysis on the PC-2Z-2MI (Table \ref{table:R2}) AM. Results are illustrated for the number of analogues on the first and second level of analogy, along with the results of the sequential calibration (red cross).}
	\label{figure:monte_carlo_r2}
\end{figure}
